---
title: "project prep quizz"
output: html_document
---


```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)

# This file is a sandbox. It should contain explorations with the dataset, along with useful comments for each exploration.

# It is important that each sanbox section should be documented of its purpose and methods, and should not spam the whole document (use filter, head, tail, etc.).

# The dataset of info on colleges listed
(college_ds = read.csv("data/projectdatamain.csv"))

# Creating blocks with include=FALSE can make space to leave comments per section, like this one.
```

```{r, visualize college_ds}
# See the dataset of the best and worst 10 rankings of colleges
head(college_ds, 10)
tail(college_ds, 10)

# Plot the dataset of median SAT and median ACT per college into the reported early career earnings in that college.
# SAT score has a much higher range than ACT, so the graph looks more "continuous"
plot(college_ds$Median.SAT, college_ds$Early.career.earnings)
# ACT score has less range, so the graph looks "discrete"
plot(college_ds$Median.ACT, college_ds$Early.career.earnings)
```
```{r}
college_ds_no_na = subset(college_ds, !is.na(Median.SAT) & !is.na(Median.ACT))
new <- na.omit(college_ds_no_na)
```

```{r}
college_ds_no_na$Median.ACT[1]
```

```{r}
hist(college_ds_no_na$Median.ACT)
#hist(college_ds_no_na$Median.ACT)
#hist(college_ds_no_na$Early.career.earnings)
summary(college_ds_no_na);summary(college_ds_no_na$Median.SAT);summary(college_ds_no_na$Median.ACT)
```

In our project, we will investigate whether SAT/ACT will contribute to the early career earning. WE have plotted out 2 plots of median SAT vs early career earning and median ACT vs early career earning. WE found out that there is a relationhsip between median ACT/SAT vs early career earning since both plots are increasing. WE will get into the detail about do the 3 variables interact with each other throgh linear regression model, and we may get anothor predict of predeiction of ACT and SAT if we have sufficient time. 
