---
title: "Project Sandbox"
author: "Hung Tran, Linh Ta"
date: "6/17/2020"
output: pdf_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
# This file is a sandbox. It should contain explorations with the dataset, along with useful comments for each exploration.
# It is important that each sanbox section should be documented of its purpose and methods, and should not spam the whole document (use filter, head, tail, etc.).
# The dataset of info on colleges listed
(college_ds = read.csv("project_data.csv"))
# Creating blocks with include=FALSE can make space to leave comments per section, like this one.
```

```{r, visualize college_ds}
# See the dataset of the best and worst 10 rankings of colleges
head(college_ds, 10)
tail(college_ds, 10)
# Plot the dataset of median SAT and median ACT per college into the reported early career earnings in that college.
# SAT score has a much higher range than ACT, so the graph looks more "continuous"
plot(college_ds$Median.SAT, college_ds$Early.career.earnings)
# ACT score has less range, so the graph looks "discrete"
plot(college_ds$Median.ACT, college_ds$Early.career.earnings)
```

```{r}
college_ds_predict = subset(college_ds, !is.na(Median.SAT) | !is.na(Median.ACT))
```

```{r, filter rows with both median SAT and median ACT are NAs}
# Get rows that have no NA, or only one of SAT, ACT is NA. Omit if both is NA.
college_ds_f = subset(college_ds, !is.na(Median.SAT) & !is.na(Median.ACT))
college_ds_predict = subset(college_ds, !is.na(Median.SAT) | !is.na(Median.ACT))
corr_c_ds_f = cor(college_ds_f$Median.ACT, college_ds_f$Early.career.earnings)
# college_ds_no_na = subset(college_ds, !(is.na(Median.SAT) & is.na(Median.ACT)))
# Omit the row where ANY column of (SAT, ACT) is NA.
college_ds_no_na = subset(college_ds, !is.na(Median.SAT) & !is.na(Median.ACT))
```

```{r, predict NA ACT}
plot(college_ds_no_na$Median.SAT, college_ds_no_na$Median.ACT)
predict_ACT_lm = lm(college_ds_no_na$Median.ACT ~ college_ds_no_na$Median.SAT)
```

```{r}
hist(college_ds_no_na$Median.SAT)
hist(college_ds_no_na$Median.ACT)
hist(college_ds_no_na$Early.career.earnings)
summary(college_ds_no_na$Median.SAT); summary(college_ds_no_na$Median.ACT); summary(college_ds_no_na$Early.career.earnings)
```

In our project, we will investigate whether SAT/ACT will contribute to the early career earning. WE have plotted out 2 plots of median SAT vs early career earning and median ACT vs early career earning. WE found out that there is a relationhsip between median ACT/SAT vs early career earning since both plots are increasing. WE will get into the detail about do the 3 variables interact with each other throgh linear regression model, and we may get anothor predict of predeiction of ACT and SAT if we have sufficient time. 

```{r}
# find out if there is a strong, fair, or weak correlation between median SAT/ACT with early career earning. 
cor(college_ds_no_na$Median.SAT, college_ds_no_na$Early.career.earnings)
lg.SAT <- lm(college_ds_no_na$Median.SAT~college_ds_no_na$Early.career.earnings)
summary(lg.SAT)
cor(college_ds_no_na$Median.ACT, college_ds_no_na$Early.career.earnings)
lg.ACT <- lm(college_ds_no_na$Median.ACT~college_ds_no_na$Early.career.earnings)
summary(lg.ACT)
```

